\papertitle

### 2012-10-12 manuscript.tex

%TODO all
The power, size, and weight constraints of micro air vehicle (MAV) 
platforms significantly limit on-board sensing and computational 
resources, and thus the complexity of the control and state estimation 
algorithms which can be executed on-board. These constraints are 
particularly severe for flapping wing MAVs, a class of MAVs that have inherently superior 
safety, efficiency, and noise profile to rotor craft MAVs, but at the 
expense of payload weight.
%Intro portion about previous works in ornithopter coorperative control/
%modeling ( won't necessarily stay in this spot)

Autonomous control of flapping winged MAVs is a complex undertaking, because
of the non-linear flight dynamics and underactuation of the system due to size
constraints. Many of the methods for controlling these platforms make
extensive use of GPS in outdoor environments [CITATIONS] and extensive motion
capture systems in indoor environments. While operating indoors, using GPS to 
estimate the pose of the MAV is not possible, and motion capture requires expensive
and stationary modification of the environment. The power and payload limits on MAVs
make on-board sensing difficult, so multi-agent cooperative control schemes are 
apt solutions.

@@

%----------------------------------------------------------------------------%
\subsection{H$^2$Bird Ornithoper MAV}
% humphrey
In order to conduct these experiments on cooperation, we designed a new
flapping-wing MAV, known as the H$^2$Bird. Built around the Silverlit I-Bird 
RC flyer power train and clap-fling wings [FOOTNOTE], the H$^2$Bird's wingspan
is 26.5 cm and it has a flight weight of 13 grams. A tail propeller and 
servo-controlled tail elevator provide control in the yaw and pitch axes. The 
on-board electronics package consists of a 40 MIPS microprocessor, 6 DOF IMU, 
IEEE 802.15.4 radio, VGA camera, and motor drivers, all powered by a 90 mAh 
lithium polymer battery [FOOTNOTE]. In routine flight, the H$^2$Bird averages 
a ground speed of 1.2 m/s and operates for approximately 10 minutes.
%TODO footnote for Silverlit I-Bird
%TODO footnote for ImageProc

@@

The high pitch angles H$^2$Bird achieves in routine flight distinguishes it 
from other MAVs. Euler angle parametrizations of the vehicle orientation 
suffer from singularities around these high pitch angles, so we instead 
represent the vehicle orientation with quaternions. An additional benefit of 
the quaternion representation its ability to represent relative body and 
world coordinate angular displacements compactly with quaternion 
multiplication.

Given a reference quaternion $q$, we define the error $q_e$ as the rotation 
required to reach the reference pose from the measured pose (Eq.~\ref{eq:quat_error}). 
\begin{equation}
\label{eq:quat_error}
q_e = q'\otimes q_r
\end{equation}
We then convert this error quaternion to an angle axis, and use this 
representation as input to the PID controller 
(Eqs.~\ref{eq:quat_angle} and~\ref{eq:quat_linearize}). 
\begin{equation}
\label{eq:quat_angle}
\alpha = 2\arccos(q_{e,w})
\end{equation}
\begin{equation}
\label{eq:quat_linearize}
Q_e = \alpha*q_e/\sin(\alpha /2)
\end{equation}

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/block_diagrams.pdf}
\caption{Overall block diagram of the cooperative control system.}
\label{fig:block_diagram}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments}
%TODO humphrey

\begin{figure}[!tb]
\centering
\includegraphics[width=\linewidth]{figures/experiment_cartoon.pdf}
\caption{Conceptual sketch of experimental environment.}
\label{fig:experiment_cartoon}
\end{figure}
%TODO label experiment cartoon

@@

%----------------------------------------------------------------------------%
\subsection{Visual Servoing}
%TODO cameron

>>>>

%TODO all
The power, size, and weight constraints of micro air vehicle (MAV) 
platforms significantly limit on-board sensing and computational 
resources, and thus the complexity of the control and state estimation 
algorithms which can be executed on-board. These constraints are 
particularly severe for flapping wing MAVs, a class of MAVs that have inherently superior 
safety, efficiency, and noise profile to rotor craft MAVs, but at the 
expense of payload weight.

%Intro portion about previous works in ornithopter coorperative control/
%modeling ( won't necessarily stay in this spot)
Modeling and control of flapping wing MAVs is a well studied subject. 
Shigeoka discusses velocity and altitude control in
~\cite{Shigeoka:ornithopter}. In~\cite{delfly:design} deCroon et al. %TODO sentence fragment
In contrast, there is little previous work on guidance of flapping wing 
MAVs. Baek demonstrated altitude control with an external 
camera~\cite{baek:altitude}. de Croon et al. demonstrated obstacle avoidance 
with an onboard camera and offboard processing~\cite{delfly:avoid}. 
%[However, these papers do not study the system blah blah blah.]

Autonomous control of flapping winged MAVs is a complex undertaking because
of the non-linear flight dynamics and underactuation of the system due to size
constraints. Many of the methods for controlling these platforms make
extensive use of GPS in outdoor environments [CITATIONS] and extensive motion
capture systems in indoor environments. While operating indoors, using GPS to 
estimate the pose of the MAV is not possible, and motion capture requires expensive
and stationary modification of the environment. The power and payload limits on MAVs
make on-board sensing difficult, so multi-agent cooperative control schemes are 
apt solutions.

@@

%----------------------------------------------------------------------------%
\subsection{H$^2$Bird Ornithoper MAV}
% humphrey
In order to conduct these experiments on cooperation, we designed a new
flapping-wing MAV, known as the H$^2$Bird. Built around the Silverlit I-Bird 
RC flyer power train and clap-fling 
wings\footnote{\url{http://www.silverlit-flyingclub.com/wingsmaster/}}, 
the H$^2$Bird's wingspan is 26.5 cm and it has a flight weight of 13 grams. A 
tail propeller and servo-controlled tail elevator provide control in the yaw 
and pitch axes. The on-board ImageProc 2.4\footnote{Expand! Accredit it to Stan Baek!} 
electronics package consists of a 40 MIPS microprocessor, 6 DOF IMU, 
IEEE 802.15.4 radio, VGA camera, and motor drivers, all powered by a 90 mAh 
lithium polymer battery. In routine flight, the H$^2$Bird averages 1.2 m/s 
ground speed, and can operate for approximately 10 minutes.
%TODO footnote for ImageProc

@@

The high pitch angles H$^2$Bird achieves in routine flight distinguishes it 
from other MAVs. Baek~\cite{baek:tracking} 
demonstrated control on a similar vehicle using PID and an Euler angle
parameterization of orientation. However, Euler angle parameterizations of the vehicle orientation 
suffer from singularities around these high pitch angles, so we instead 
represent the vehicle orientation with quaternions. An additional benefit of 
the quaternion representation its ability to represent relative body and 
world coordinate angular displacements compactly with quaternion 
multiplication.

Our implementation of quaternion-based control is similar to Knoebe's~\cite{knoebe:quatcontrol}:
Given a reference quaternion $q$, we define the error $q_e$ as the rotation 
required to reach the reference pose from the measured pose (Eq.~\ref{eq:quat_error}). 
\begin{equation}
\label{eq:quat_error}
q_e = q'\otimes q_r
\end{equation}
We then convert this error quaternion to an angle axis, and use this 
representation as input to the PID controller 
(Eqs.~\ref{eq:quat_angle} and~\ref{eq:quat_linearize}). 
\begin{equation}
\label{eq:quat_angle}
\alpha = 2\arccos(q_{e,w})
\end{equation}
\begin{equation}
\label{eq:quat_linearize}
Q_e = \alpha*q_e/\sin(\alpha /2)
\end{equation}

@@

%TODO trim PDF
\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/block_diagrams.pdf}
\caption{Overall block diagram of the cooperative control system.}
\label{fig:block_diagram}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments}
%TODO ryan
The task we chose to test our cooperative visual servoing system with is a 
simple target seeking one: the H$^2$Bird must fly through a specified obstacle,
in this case, a wooden frame meant to simulate a window. As the H$^2$Bird does
cannot detect the target on its own, it depends on remote guidance from the
base station. Ground truth data was collected via a motion capture system in
the test room. A sketch of the experimental setup is shown below in Fig.~\ref{fig:experiment_cartoon}.

% TODO clarify or roll into paragraph
Trials were run as follows:
\begin{enumerate}
\item The window is identified by a user. 
\item The H$^2$Bird is released in view of the camera by hand.
\item The H$^2$Bird attempts to fly to the window with remote guidance from
the base station.
\end{enumerate}

% TODO Fill in test # per battery
In total, [50+] good trials were run over a variety of starting positions. 
Variations in the H$^2$Bird hand launch caused the system to respond very 
differently for similar initial conditions. In addition, the H$^2$Bird 
battery was changed approximately every [10] tests, adding more variation to
the H$^2$Bird performance by affecting the motor power output. The effects of 
these noisy factors is considered in Section ~\ref{sec:performance}.

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/experiment_cartoon.pdf}
\caption{Conceptual sketch of experimental environment.}
\label{fig:experiment_cartoon}
\end{figure}
%TODO label experiment cartoon

@@

%----------------------------------------------------------------------------%
\subsection{Visual Servoing}
\label{sec:visual_servoing}
%TODO cameron
